% ---------------------- GLOSSARY TERMS --------------------------------

\newglossaryentry{linux}{
    name=Linux,
    description={is a generic term referring to the family of Unix-like computer operating systems that use the Linux kernel},
    plural=Linuces
}

\newglossaryentry{matrix}{
    name={matrix},
    plural={matrices},
    description={rectangular array of quanttities}
}

\newglossaryentry{frustum}{
    name={frustum},
    plural={frusta},
    description={In geometry: defined as the portion of a solid, normally a cone or pyramid, that lies between two parallel planes.
    In computer graphics: the viewing frustum is the three-dimensional region which is visible on screen.}
}

\newglossaryentry{point_cloud}{
    name={point cloud},
    plural={point clouds},
    description={A set of points in some reference system.
        In a three dimension corrdination system, the points typical represent the cartesian position of the external surface of an object.
    Frequently generated from a 3D scanning process, these points are rarely used directly but rather converted into a surface representation, such as a polygonal mesh.}
}

\newglossaryentry{implicit_shape}{
    name={implicit shape},
    plural={implicit shapes},
    description={In mathematics: an implicit shape or surface is the surface in Euclidean space defined by an equation \( F(x, y, z) = 0\).
    The implicit surface is the zero set of the function \( F \), and is termed \textit{implicit} as the function is not solved for \( x, y, \text{ or } z \).}
}

\newglossaryentry{polygon}{
    name={polygon},
    plural={polygons},
    description={The area of a plane bounded by straight segments, called edges, which intersect only at their endpoints, called vertices.
    Each vertex belongs to exactly two edges and similarly each edge has exactly two vertices.}
}

\newglossaryentry{MAT}{
    name={medial axis transform},
    description={The medial axis is the set of all point shaving more than one closest point on the objects boundary.
    The medial axis along with the associated radius function of the maximally inscribed discs is called the medial axis transform.}
}

\newglossaryentry{CAD}{
    name={computer aided design},
    description={The use of computer software to create mechanical design drawings}
}
